### 2016-01-27 mcmc.tex
cite numpy

\begin{problem}
Look up (or choose) definitions for the mean, variance, skewness,
and kurtosis of a distribution.
Also look up or compute the analytic values of these four statistics
for a top-hat (uniform) distribution.
Write a computer program that uses some standard package (such as
\project{numpy}\note{HOGG CITE NUMPY}) to generate $K$ random numbers
$x$ from a uniform distribution in the interval $0<x<1$.
Now use those $K$ numbers to compute a the sampling estimate of the
mean, variance, skewness, and kurtosis (four estimates)
Make four plot of these four estimates as a function of $1/K$ or
perhaps $\log_2 K$, for $K=4^n$ for $n=1$ up to $n=10$ (that is,
$K=4$, $K=16$, and so on up to $K=1048576$).
Over-plot the analytic answers.
What can you conclude?
\end{problem}

@@

\clearpage
\raggedright
\begin{thebibliography}{}\markright{References}
\bibitem[Box \& Draper(1987)]{box}
  Box,~G.~E.~P. \& Draper,~N.~R.\ 1987,
  \textit{Empirical Model Building and Response Surfaces},
  John Wiley \& Sons, New York, NY
  \isbn{978-0471810339}.
\bibitem[Brooks \etal(2011)]{mcmchandbook}
  Brooks,~S., Gelman~A., Jones~G., \& Meng,~X.-L., eds.\ 2011,
  \textit{Handbook of Markov Chain Monte Carlo},
  Chapman and Hall~/~CRC Press
  \isbn{978-1-4200-7941-8}.
\bibitem[Foreman-Mackey \etal(2012)]{emcee}
  Foreman-Mackey,~D., Hogg,~D.~W., Lang,~D., \& Goodman,~J.\ 2012,
  \project{emcee}: The MCMC Hammer,
  \textit{Pubs.\,Astron.\,Soc.\,Pac.}\ \textbf{125} 306--312
  \doi{10.1086/670067}
  (also \arxiv{1202.3665}).
\bibitem[Hogg \etal(2010)]{fittingaline}
  Hogg,~D.~W., Bovy,~J., \& Lang,~D., 2010,
  Data analysis recipes: Fitting a model to data,
  \arxiv{1008.4686v1}.
\bibitem[Hou \etal(2014)]{fengji}
  Hou,~F., Goodman,~J., \& Hogg,~D.~W., 2014,
  The probabilities of orbital-companion models for stellar radial velocity data,
  \arxiv{1401.6128}.
\end{thebibliography}

>>>>

\begin{problem}
Look up (or choose) definitions for the mean, variance, skewness,
and kurtosis of a distribution.
Also look up or compute the analytic values of these four statistics
for a top-hat (uniform) distribution.
Write a computer program that uses some standard package (such as
\project{numpy}\note{There isn't a full citation for this package but there is \cite{numpy}.})
to generate $K$ random numbers
$x$ from a uniform distribution in the interval $0<x<1$.
Now use those $K$ numbers to compute a the sampling estimate of the
mean, variance, skewness, and kurtosis (four estimates)
Make four plot of these four estimates as a function of $1/K$ or
perhaps $\log_2 K$, for $K=4^n$ for $n=1$ up to $n=10$ (that is,
$K=4$, $K=16$, and so on up to $K=1048576$).
Over-plot the analytic answers.
What can you conclude?
\end{problem}

@@

\clearpage
\raggedright
\begin{thebibliography}{}\markright{References}
\bibitem[Box \& Draper(1987)]{box}
  Box,~G.~E.~P. \& Draper,~N.~R.\ 1987,
  \textit{Empirical Model Building and Response Surfaces},
  John Wiley \& Sons, New York, NY
  \isbn{978-0471810339}.
\bibitem[Brooks \etal(2011)]{mcmchandbook}
  Brooks,~S., Gelman~A., Jones~G., \& Meng,~X.-L., eds.\ 2011,
  \textit{Handbook of Markov Chain Monte Carlo},
  Chapman and Hall~/~CRC Press
  \isbn{978-1-4200-7941-8}.
\bibitem[Foreman-Mackey \etal(2012)]{emcee}
  Foreman-Mackey,~D., Hogg,~D.~W., Lang,~D., \& Goodman,~J.\ 2012,
  \project{emcee}: The MCMC Hammer,
  \textit{Pubs.\,Astron.\,Soc.\,Pac.}\ \textbf{125} 306--312
  \doi{10.1086/670067}
  (also \arxiv{1202.3665}).
\bibitem[Hogg \etal(2010)]{fittingaline}
  Hogg,~D.~W., Bovy,~J., \& Lang,~D., 2010,
  Data analysis recipes: Fitting a model to data,
  \arxiv{1008.4686v1}.
\bibitem[Hou \etal(2014)]{fengji}
  Hou,~F., Goodman,~J., \& Hogg,~D.~W., 2014,
  The probabilities of orbital-companion models for stellar radial velocity data,
  \arxiv{1401.6128}.
\bibitem[van~der~Walt \etal(2011)]{numpy}
  van~der~Walt,~S., Colbert,~S.~C., and Varoquaux,~G., 2011,
  The NumPy Array: A structure for efficient numerical computation,
  \textit{Computing in Sci.\ \& Eng.}\ \textbf{13}, 22--30
  \doi{10.1109/MCSE.2011.37}.
\end{thebibliography}
